Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study

### 2024-11-06 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.tex
x paper

>>>>

\paragraph{2.2.2 Number of fixations per minute (AOI
others)}\label{number-of-fixations-per-minute-aoi-others}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max number of fixations per minute (AOI
others)}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 48.51 & 13.08 & 29.70 & 80.89 \\
Expert & 40 & 52.79 & 15.14 & 18.85 & 99.66 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_others-1.pdf}

\paragraph{t-test \& effect size ``Number of fixation'' (AOI
others)}\label{t-test-effect-size-number-of-fixation-aoi-others}

data: df\_aoi\_others\(Others_number_fixation_min[df_aoi_others\)Group
== ``Expert''{]} and
df\_aoi\_others\(Others_number_fixation_min[df_aoi_others\)Group ==
``Novice''{]} t = 1.3722, df = 80, p-value = 0.1738 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -1.927317 10.487650 sample estimates: mean of x
mean of y 52.79350 48.51333

{[}1{]} 0.3 attr(,``magnitude'') {[}1{]} ``small''
